Plant-pollintor networks worldwide are composed by the same specific building

### 2021-06-15 Draft/Draft.Rmd
Adding refs and functional groups names

The interaction between plants and pollinators can be studied at different scales, from species level interactions (micro-scale) to the full network structure (macro-scale). Research of the network structure have proven common invariant structural properties across them including a degree distribution that decays as a power law [@jordano2003](idem, aqui molaria citar el original del 98, si no me equivoco), nestedness [@jordano2003](Aqui la cita seria Bascompte PNAS), or the imbalance between plants and pollinators with approximately four times more pollinator species [@vazquez2009](Esta no estoy seguro no sea un artefacto del muestreo... quizas la quitamos? buscamos otra?). In addition, species phenological overlap, morphological matching and species abundances have been shown to be determinant for the understanding of pairwise plant-pollinator interactions [@bartomeus2016, @stang2006; @peralta2020]. However, both species level information or an holistic view of the full network involves missing relevant information for the understanding of ecological processes [@simmons2019].

Indirect interactions (i.e., motifs), commonly referred as the building blocks that depict subsets of interactions of the network [@milo2002], are a widespread phenomenon in ecological communities [@strauss1991]. For instance, plant species can facilitate or compete for pollinator's visitation when two species are visited by the same pollinator [@Gazoul200XJEcol?]. Despite the relevance of indirect interactions in ecological communities, plant-pollinator research often fails to finely capture those indirect interactions with the traditional analytical tools that condense the information either by species (e.g. interaction frequency) or in single topological indices (e.g. nestedness). Nonetheless, the emerging framework of network motifs in plant-pollinator research allows to consider both direct and indirect interactions [@simmons2019]. The study of @simmons2020 have shown that the different processes that govern species interactions (e.g., species abundances versus trait-matching) can lead to different patterns of indirect interactions. However, we still ignore which are the general patterns observed in the distribution of plant-pollinator motifs worldwide.

Motifs are abstract representations often decoupled from species ecology. Hence, linking the structural properties of the meso-scale with the species ecology can help the understanding of ecological processes. For instance, different motifs can have different ecological meanings [@simmons2019] and the position within a motif can determine the species functional role [@stouffer2012; @baker2015]. However, it is unclear if species ecological and life history traits strongly determines its role within the network of interactions [@coux201X?]. For example, bees are more specialized foragers [Jose, aquí por ejemplo, pueden decir que abejas pequeñas y generalistas, pueden comportarse muy diferente que grandes y especialistas... si tienes una lista de pollintors, con su familia, pasamela, y le hecho un ojo](), usually alble to open complex zygomorphic flowers which are not accessible to fly pollinators. How this different behaviors translate into their interaction topology is unknown. Similarly, recent empirical findings indicate that the meso-scale is the best descriptor of plant reproductive success [@allen2021], but little is known on how plants reproductive strategies shape their position within the network of interactions. Although some studies have evaluated plant reproductive strategies in plant-pollinator networks [@tur2013; @lazaro2020], they are often overlooked in a community context [@devaux2014] and rarely incorporated into plant-pollinator network studies. Hence, exploring how the main plant reproductive strategies integrate with the emergent motif framework can shed light on key aspects of ecosystem functioning.

@@

The hierarchical cluster analysis divided the dataset with 1506 species and 15 traits into five different clusters with different and overlapping characteristics (Figure S1). The subset of plant species used in this study were distributed evenly across these different five groups (see Figure S1). The first cluster [...]

@@

ggplot(ggd1,offset_labels=-0.05) + theme(panel.grid.major = element_blank(),
 axis.text = element_blank(),axis.title = element_blank()) +
  ggtitle("Plant functional groups")+
  theme(plot.title = element_text(hjust = 0.5, vjust = -2,size = 20,face="bold"))

>>>>

The interaction between plants and pollinators can be studied at different scales, from species level interactions (micro-scale) to the full network structure (macro-scale). Research of the network structure have proven common invariant structural properties across them including a degree distribution that decays as a power law [@jordano1987], nestedness [@bascompte2003], or the higher number of pollinator species than plant species [@bluthgen2007]. In addition, species phenological overlap, morphological matching and species abundances have been shown to be determinant for the understanding of pairwise plant-pollinator interactions [@bartomeus2016; @stang2006; @peralta2020]. However, both species level information or an holistic view of the full network involves missing relevant information for the understanding of ecological processes [@simmons2019].

Indirect interactions (i.e., motifs), commonly referred as the building blocks that depict subsets of interactions of the network [@milo2002], are a widespread phenomenon in ecological communities [@strauss1991]. For instance, plant species can facilitate or compete for pollinator's visitation when two species are visited by the same pollinator [@ghazoul2006]. Despite the relevance of indirect interactions in ecological communities, plant-pollinator research often fails to finely capture those indirect interactions with the traditional analytical tools that condense the information either by species (e.g. interaction frequency) or in single topological indices (e.g. nestedness). Nonetheless, the emerging framework of network motifs in plant-pollinator research allows to consider both direct and indirect interactions [@simmons2019]. The study of @simmons2020 have shown that the different processes that govern species interactions (e.g., species abundances versus trait-matching) can lead to different patterns of indirect interactions. However, we still ignore which are the general patterns observed in the distribution of plant-pollinator motifs worldwide.

Motifs are abstract representations often decoupled from species ecology. Hence, linking the structural properties of the meso-scale with the species ecology can help the understanding of ecological processes. For instance, different motifs can have different ecological meanings [@simmons2019] and the position within a motif can determine the species functional role [@stouffer2012; @baker2015]. However, it is unclear if species ecological and life history traits strongly determines its role within the network of interactions [@coux2016]. For example, bees are more specialized foragers [Jose, aquí por ejemplo, pueden decir que abejas pequeñas y generalistas, pueden comportarse muy diferente que grandes y especialistas... si tienes una lista de pollintors, con su familia, pasamela, y le hecho un ojo](), usually alble to open complex zygomorphic flowers which are not accessible to fly pollinators. How this different behaviors translate into their interaction topology is unknown. Similarly, recent empirical findings indicate that the meso-scale is the best descriptor of plant reproductive success [@allen2021], but little is known on how plants reproductive strategies shape their position within the network of interactions. Although some studies have evaluated plant reproductive strategies in plant-pollinator networks [@tur2013; @lazaro2020], they are often overlooked in a community context [@devaux2014] and rarely incorporated into plant-pollinator network studies. Hence, exploring how the main plant reproductive strategies integrate with the emergent motif framework can shed light on key aspects of ecosystem functioning.

@@

The hierarchical cluster analysis divided the dataset with 1506 species and 15 traits into five different clusters with different and overlapping characteristics (Figure S1). The subset of plant species used in this study (N = 503) were distributed evenly across these different larger five groups (see Figure S1). The first cluster "short-lived selfers"

@@

ggplot(ggd1,offset_labels=-0.05) + theme(panel.grid.major = element_blank(),
 axis.text = element_blank(),axis.title = element_blank()) +
  ggtitle("Plant functional groups")+
  theme(plot.title = element_text(hjust = 0.5, vjust = -2,size = 20,face="bold"))+
  annotate("text", x=140, y=1.65, label= "Perennials self-incompatible large flowers ", size=2.5)+
  annotate("text", x=380, y=2.15, label= "Tall plants small unisexual flowers", size=2.5) +
  annotate("text", x=600, y=3.85, label= "Short-lived selfers", size=2.5) +
  annotate("text", x=1400, y=2.05, label= "Short-lived non-selfers \n long zygomorphic flowers", size=2.5) +annotate("text", x=950, y=2.05, label= "Small non-selfers perennials", size=2.5)
